PineAPPL:\\ combining EW and QCD corrections for PDF fits

### 2020-08-20 paper/sec-results.tex
two comments of stefan's addressed

The NLO QCD+EW corrections always lead to a reduction of the cross section in
comparison to the NLO QCD prediction. The size of this shift is comparable to
the data uncertainty at small values of $M_{\ell\bar\ell}$, and rapidly becomes
negligible with respect to it as the value of the invariant mass increases
and the data uncertainty blows up. This fact suggests a couple of observations
in light of the inclusion of EW corrections in a fit of PDFs. First, the
description of the more precise bins in the low invariant mass range is likely
to change, and will possibly become more accurate should the inclusion of EW
corrections improve the data/theory agreement. Second, the kinematic cut that
excludes any data point at large $M_{\ell\bar\ell}$ can be safely removed: any
shift in the predictions induced by the more accurate NLO QCD+EW theory is
likely to be easily accommodated by the large data uncertainty. As the data
will become more precise, in particular thanks to the increased Run-II LHC
luminosity, this conclusion might not continue to hold.

@@

The way in which NLO QCD+EW corrections affect the theoretical prediction for
the double differential cross section (with respect to its counterpart accurate
to NLO QCD) depends on the invariant mass bin. In the
$\SI{45}{\giga\electronvolt}<M_{\ell\bar\ell}<\SI{60}{\giga\electronvolt}$ region, they enhance the value of the cross
section by about \SI{11}{\percent} across all the rapidity range; in the
$\SI{60}{\giga\electronvolt}<M_{\ell\bar\ell}<\SI{120}{\giga\electronvolt}$ region, they suppress the value of the cross
section by about \SI{2}{\percent}, again across all the rapidity range; in the
$\SI{120}{\giga\electronvolt}<M_{\ell\bar\ell}<\SI{200}{\giga\electronvolt}$ bin, the suppression is around \SIrange{4}{5}{\percent}; and in
the $\SI{200}{\giga\electronvolt}<M_{\ell\bar\ell}<\SI{1500}{\giga\electronvolt}$ bin, the suppression increases further to
about \SIrange{6}{7}{\percent} for rapidities $y_{\ell\bar\ell}<2.0$ and up to \SIrange{20}{40}{\percent} at forward
rapidities. For this reason, for instance, the data points with
$M_{\ell\bar\ell}>\SI{200}{\giga\electronvolt}$ and $y_{\ell\bar\ell}>2.2$ were not included in the
NNPDF3.1 analysis~\cite{Ball:2017nwa}.

>>>>

The NLO QCD+EW corrections always lead to a reduction of the cross section in
comparison to the NLO QCD prediction. The size of this shift is comparable to
the data uncertainty at small values of $M_{\ell\bar\ell}$, and rapidly becomes
negligible with respect to it as the value of the invariant mass increases
and the data uncertainty blows up. This fact suggests a couple of observations
in light of the inclusion of EW corrections in a fit of PDFs. First, the
description of the more precise bins in the low invariant mass range is likely
to change, and will possibly become more accurate should the inclusion of EW
corrections improve the data/theory agreement. Second, the kinematic cut that
excludes any data point at large $M_{\ell\bar\ell}$ can be safely removed: any
shift in the predictions induced by the more accurate NLO QCD+EW theory is
likely to be easily accommodated by the large data uncertainty. However, 
this conclusion might not continue to hold: first, data
will become more precise, in particular thanks to the increased Run-II LHC
luminosity. Second, both EW corrections and PI contributions are expected to
grow larger at \SI{13}{\tera\electronvolt}, making their impact more relevant.

@@

The way in which NLO QCD+EW corrections affect the theoretical prediction for
the double differential cross section (with respect to its counterpart accurate
to NLO QCD) depends on the invariant mass bin. In the
$\SI{45}{\giga\electronvolt}<M_{\ell\bar\ell}<\SI{60}{\giga\electronvolt}$ region, they enhance the value of the cross
section by about \SI{11}{\percent} across all the rapidity range. This is mostly due to photon-radiation effects
on events with $M_{\ell\bar\ell}\simeq M_\mathrm{Z}$ at the Born, for which the invariant mass is shifted to lower 
values. In the 
$\SI{60}{\giga\electronvolt}<M_{\ell\bar\ell}<\SI{120}{\giga\electronvolt}$ region, EW corrections suppress the value of the cross
section by about \SI{2}{\percent}, again across all the rapidity range; in the
$\SI{120}{\giga\electronvolt}<M_{\ell\bar\ell}<\SI{200}{\giga\electronvolt}$ bin, the suppression is around \SIrange{4}{5}{\percent}; and in
the $\SI{200}{\giga\electronvolt}<M_{\ell\bar\ell}<\SI{1500}{\giga\electronvolt}$ bin, the suppression increases further to
about \SIrange{6}{7}{\percent} for rapidities $y_{\ell\bar\ell}<2.0$ and up to \SIrange{20}{40}{\percent} at forward
rapidities. For this reason, for instance, the data points with
$M_{\ell\bar\ell}>\SI{200}{\giga\electronvolt}$ and $y_{\ell\bar\ell}>2.2$ were not included in the
NNPDF3.1 analysis~\cite{Ball:2017nwa}.
